\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-17 NAR_DRAFT.tex
making changes to wes figure caption

\rngcomment{Got here...}
\bkmcomment{No currently published paper has numbered equations, and it is not mentioned in the guidelines. I am using their template for numbered and non-numbered equations.}
We model the observed mutation profile $S$ (Figure~\ref{NAR-sigfig}\textbf{A} throught \textbf{C}) as multinomial with parameter $\boldsymbol{\pi} = \{\pi_{m,c}\}$.
Each element of $\boldsymbol{\pi}$ represents the expected proportion of mutations that are to allele $m$ and in context $c$.
In a tumor with many high-confidence observed mutations, $\boldsymbol{\pi}$ could be estimated directly from the observed mutation profile $S$.
But in practice many entries in $\boldsymbol{\pi}$ would then have zero weight.
We thus model $\mathrm{p}(\mathrm{S})$ as Dirichlet-multinomial with pseudo-count hyper-parameter $\boldsymbol{\alpha}$, 
\begin{equation}
\begin{aligned}
  \boldsymbol{\pi} \mid \boldsymbol{\alpha} &\sim \textrm{Dirichlet}(\boldsymbol{\alpha}) \\
  \mathrm{S} \mid \boldsymbol{\pi} & \sim \textrm{Multinomial}(\boldsymbol{\pi}).
\end{aligned}
\end{equation}
In \batcave we use the symmetric non-informative hyper-parameter $\boldsymbol{\alpha} = \boldsymbol{1}$, so a priori mutation is equally likely in any context.

@@

  \begin{figure*}
    \begin{center}
    \includegraphics{figures/fig_wes.pdf}
    \end{center}
    \caption{Model performance.
    \textbf{(A)} Precision-recall curves and \textbf{(B)} Receiver operating characteristic curves for 3 mutation signatures.
    Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
    A perfectly calibrated model would generate the diagonal line. Precision-recall curves for real data \textbf{(E)} and \textbf{(F)}.}
  \label{NAR-wes_fig}
  \end{figure*}

>>>>

\rngcomment{Got here...}
\bkmcomment{No currently published paper has numbered equations, and it is not mentioned in the guidelines. I am using their template for numbered equations and made all equations numbered for consistency.}
We model the observed mutation profile $S$ (Figure~\ref{NAR-sigfig}\textbf{A} throught \textbf{C}) as multinomial with parameter $\boldsymbol{\pi} = \{\pi_{m,c}\}$.
Each element of $\boldsymbol{\pi}$ represents the expected proportion of mutations that are to allele $m$ and in context $c$.
In a tumor with many high-confidence observed mutations, $\boldsymbol{\pi}$ could be estimated directly from the observed mutation profile $S$.
But in practice many entries in $\boldsymbol{\pi}$ would then have zero weight.
We thus model $\mathrm{p}(\mathrm{S})$ as Dirichlet-multinomial with pseudo-count hyper-parameter $\boldsymbol{\alpha}$, 
\begin{equation}
\begin{aligned}
  \boldsymbol{\pi} \mid \boldsymbol{\alpha} &\sim \textrm{Dirichlet}(\boldsymbol{\alpha}) \\
  \mathrm{S} \mid \boldsymbol{\pi} & \sim \textrm{Multinomial}(\boldsymbol{\pi}).
\end{aligned}
\end{equation}
In \batcave we use the symmetric non-informative hyper-parameter $\boldsymbol{\alpha} = \boldsymbol{1}$, so a priori mutation is equally likely in any context.

@@

  \begin{figure*}
    \begin{center}
    \includegraphics{figures/fig_wes.pdf}
    \end{center}
    \caption{Model performance.
    \textbf{(A)} Precision-recall curves and \textbf{(B)} Receiver operating characteristic curves for 3 mutation signatures.
    Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
    A perfectly calibrated model would generate the diagonal line. 
    \textbf{(E)}--\textbf{(F)} Precision-recall curves for real data.}
  \label{NAR-wes_fig}
  \end{figure*}
